*Symbiodinium* communities in reef corals of St. John, U.S.V.I. (2012)

### 2016-08-15 analysis/STJ2012_analysis.Rmd
add main findings

>>>>

# Main findings
1. Symbiont communities are generally consistent with previous work on these species in the Caribbean, but high-throughput sequencing provides a much **more complete picture** of these communities’ composition.
2. South shore *P. furcata* are more likely to have clade A instead of C, and *S. siderea* more likely to have clade D instead of C.
3. **Within-sample OTU clustering** is more appropriate than clustering across samples.
4. We can apply **new types of analysis** with this much data, including network analysis and statistical tests on beta diversity.
